

\documentclass{resume} 
\renewcommand{\baselinestretch}{1.0}
\setlength{\parskip}{0.2em}

\usepackage[left=0.5in,top=0.3in,right=0.5in,bottom=0.25in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{0.5\textwidth}\rlap{#1}}
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Chaeyoung Kim} % Your name
\address{1988 Martin Luther King Jr Way 408 Berkeley CA 94704} % Your address
%\address{123 Pleasant Lane \\ City, State 12345} % Your secondary addess (optional)
\address{(510) 501-3142 chaeyoung\_kim@berkeley.edu} % Your phone number and email

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf UNIVERSITY OF CALIFORNIA-BERKELEY 
} \hfill {\em Expected graduation, May 2020} 
\\ B.A. Economics
\begin{itemize}
    \item GPA: 3.70
    \item Relevant Courses: Economic Analysis-Micro, Economic Analysis-Macro, Foundations of Data Science, Computational Structures in Data Science, Introduction to Probability and Statistics, Industrial Organization and Public Policy, Data Science Skill Decal 
\end{itemize}
\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Work Experience}
{\bf Summer Marketing Internship}\hfill{Jul 2017}{}
\\Cebien - Gwangju, Gyeonggi-do, Korea
\begin{itemize}
    \item Proactively identified and solved social marketing strategy problems that impact business brand image. 
    \item Developed interesting and engaging content for social media platforms including Facebook, Instagram, and blog.
    \item Increased social media reach by having active communication with prospective customers.
\end{itemize}

\\{\bf Summer Internship: Art Fair Event Assistant}\hfill {Jul 2016}{}
\\Kwangjuyo - Icheon, Gyeonggi-do, Korea
\begin{itemize}
    \item Greeted incoming guests, accepted payments, directed facility locations.
    \item Generated leads for new sales with a detailed explanation of artworks to customers.
    \item Maintained visually appealing and effective displays for the entire booth.
\end{itemize}

\end{rSection}
%------------------------------------------------ Extracurricular and Leadership Experience
%---------------------------------------
\begin{rSection}{ Extracurricular and Leadership Experience}
{\bf Economics Academic Affairs Committee	}\hfill{Feb 2019 to present
}{}
\\{\bf UC Berkeley Undergraduate Economics Association (UEA)} - Berkeley, CA
\begin{itemize}
    \item Running UEA’s academically related activities including workshop, professor luncheons, Federal Reserve tours, and CalCentral advising.
    \item Participated in weekly meetings where committee members discuss current economic topics.
    \item Collaborated with the Professional Affairs Committee and consulting team to work on economic projects.
\end{itemize}

\\{\bf UNICEF Club Volunteer Coordinator}\hfill {Aug 2016 to Dec 2017}{}
\\{\bf Diablo Valley College UNICEF Club} - Pleasant Hill, CA
\begin{itemize}
    \item Contacted with nonprofit organizations and schools to find volunteering opportunities.
    \item Solicited feedback from staff and volunteers to improve existing volunteer programs.
    \item Followed up with staff to assess volunteer needs and opportunities.
    \item Evaluated team member performance and offered constructive feedback.
\end{itemize}

\\{\bf Phi Beta Lambda (Business organization) Marketing Coordinator }\hfill {Aug 2016 to May 2017}{}
\\{\bf Phi Beta Lambda} - Pleasant Hill, CA
\begin{itemize}
    \item Participated in the California PBL State Business Leadership conference.
    \item Won first place out of nine teams in social media marketing presentation competition. Led the team and organized presentation.
    \item Won third place in global analysis and decision making knowledge event.
\end{itemize}
\end{rSection}


%--------------------------------------------------------------------------------
%    Skills and Projects
%-----------------------------------------------------------------------------------------------
\begin{rSection}{Skills And Projects}
{\bf Python (basic level)}: Data project about world progress (fertility and life expectancy), global poverty, a relationship between diet and disease using hypothesis test, making a classifier.\\
{\bf R (basic level)}: Statistics project using world happiness report from Gallup World Poll. Compared the effects of Economics and Politics on national happiness.\\
{\bf Microsoft Office}: Word, PowerPoint, Excel\\
{\bf Languages}: English (fluent), Korean (native), Japanese (basic level)\\


\end{rSection}
\end{document}
